{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-06-14 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

@@

@@

        \begin{definition}[a conic feasibility problem]
            Let $A\in \RR^{m\times n}$, $b \in \RR^m$
            Let $\mathcal K$ be a simple cone. 

@@

                \min_{x \in \mathcal K} \Vert Ax - b\Vert^2.

@@

        The KKT of a linear programming problem is an instance of a linear feasibility problem, with $\mathcal K$ being a cross product of one of $\RR, \RR_+, \RR_-$. 
        A feasibility semidefinite program with linear constraint can is another example. 

@@

    \section{Hoffman Bounds and infeasibility detection}
        The Hoffman error bound conditions is essential to analyzing optimization problem arises in applications with polytoptic constraints.

>>>>

    % SYMBOL SET FOR THIS CHAPTER ONLY! 
    \newcommand{\QSCNVX}{\ensuremath{q\mathcal{S}}}
    \newcommand{\QUA}{\ensuremath{\mathcal U}}
    \newcommand{\QGG}{\ensuremath{\mathcal G}}
    \newcommand{\QFG}{\ensuremath{\mathcal F}}
    \newcommand{\PEB}{\ensuremath{\mathcal E}}
    \todoinline{\noindent
        Defined special symbols/substitutes in this chapter: 
        Q-SCNVX $\QSCNVX$; QUA $\QUA$; QGG $\QGG$; QFG $\QFG$; PEB $\PEB$. 

@@

        \subsection{Characterizing Q-SCNVX functions with Hoffman's Error bound}
            Necoara et al. \cite{necoara_linear_2019}

@@

        \begin{definition}[a linear conic feasibility problem]\label{def:lcf-problem}
            Let $A\in \RR^{m\times n}$, $b \in \RR^{m\times p}$
            Let $\mathcal K \in \RR^{n \times p}$ nonempty, closed convex cone. 

@@

                \min_{X \in \mathcal K} \Vert AX - B\Vert^2_F.

@@

        The KKT of a linear programming problem is an instance of a linear feasibility problem, with $\mathcal K$ being a cross product of one of $\RR, \RR_+, \RR_-$ and $p = 1$ making $x \in \RR^{n}$. 
        A feasibility semidefinite program with linear constraint is another example. 
        \subsection{Example, linear programming is a linear conic feasibility problem}

@@

            The convergence rate can be simplified a bit. 
            On a calculator it has $4e\sqrt{2}/(2 - \sqrt{2}) \le 27$ and, $1/(16\sqrt{2 + 2e}) \ge 0.02$ so 
                \Vert z_J - z_J^+\Vert &\le \frac{27(F(z_0) - F^+)^{1/2}}{\kappa}\exp\left(
                    - \frac{K\sqrt{\kappa}}{20}

    \section{Hoffman error bound and quadratic growth}
        The Hoffman error bound conditions is essential to analyzing optimization problem arises in applications with polytoptic constraints.
